---
output: html_document
editor_options: 
  chunk_output_type: console
---
 ---
 title: "Prejudice and Narcissism"
 author: "Matthias Ziegler & Oliver Keenan"
 date: "`r format(Sys.time(), '%d %B, %Y')`"
 output:
   html_document:
   code_folding: hide
   number_sections: yes
   toc: yes
   toc_float: yes
editor_options:
 chunk_output_type: inline
---
# Preps



```{r}
library(tidyverse)
library(lavaan)
library(lmtest)
library(sandwich)
source(paste0(getwd(), "/CFA_functions_Matthias.R"))
vc <- function(x){vcovHC(x, type = "HC4")}

dat <- rio::import(paste0(getwd(),"/Study2.sav"))


dat <- dat %>% mutate(PrejT1 = furniture::rowmeans(ant_t1,sexT_t1,homo_t1,PreUK_t1),
                      PrejT0 = furniture::rowmeans(ant_t0,sexT_t0,homo_t0,PreUK_t0)) 

```


```{r}
# Regressions
dat$CN_t0 = round(dat$CN_t0)
dat$CN_t0 = as.numeric(dat$CN_t0)


mod1 <- lm(PrejT1 ~ PrejT0 + group, dat)

summary(mod1)
waldtest(mod1, vcov = vc) 


mod2 <- lm(PrejT1 ~ PrejT0 + (CN_t0) * group, dat)

summary(mod2)
waldtest(mod2, vcov = vc)
waldtest(mod1, mod2, vcov = vc) 

   

```


```{r}
# Regression table
library(sjPlot)

tab_model(mod1, mod2,  
                  string.est = "b(SE)",
                  #string.std = "β",
                  strings = c(ci = "95%CI LL,UL", stat = "t"),
                  show.se = TRUE, collapse.se = T, 
                  ci.hyphen = "&comma;",
                  title = "",
                  show.intercept = F,
                  dv.labels = c("Model 1", "Model 2", "Model 3"),
                  #show.std = F,
                  show.est = T,
                  show.stat= F,
                  col.order = c("est", "se", "ci", "stat", "p"#, #"std.est", "std.se"
                                ),
                  emph.p = F
                  ,vcov.fun = "HC4"
)
```

Model 1
```{r}
# ANOVA figure
library(emmeans)
library(rstatix)
library(broom)
library(ggpubr)
res.aov <- aov(PrejT1 ~ PrejT0 + group, dat)
res.aov <- dat %>% anova_test(PrejT1 ~ PrejT0 + group)
coeftest(res.aov, vcov = vc)
get_anova_table(res.aov)
pwc <- dat %>% 
  emmeans_test(
    PrejT1 ~ group, covariate = PrejT0,
    p.adjust.method = "bonferroni"
    )
pwc
pwc <- pwc %>% add_xy_position(x = "group", fun = "mean_se")
pwc

ggpubr::ggline(get_emmeans(pwc), x = "group", y = "emmean") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) + 
  stat_pvalue_manual(pwc, hide.ns = TRUE, tip.length = FALSE) +
  labs(x = "Training", y = "Prejudice",
    subtitle = get_test_label(res.aov, detailed = TRUE)[-2]
      ) + scale_x_discrete(labels=c('Wait-List Control', 'Mindful-Gratitude Practice'))
```

Model 2 - Simple slopes
```{r}

interactions::sim_slopes(mod2, pred = "CN_t0", modx = "group", robust = "HC4", confint = T, digits = 3) 
 

sjPlot::plot_model(mod2, type = "pred", terms = c("CN_t0", "group"), vcov.fun = "HC4", colors = c("blue", "red")) + 
  labs(x = "Collective Narcissism", y = "Prejudice", colour = "", title = "") + theme_classic() + theme(text = element_text(size = 12), legend.title = element_blank()) + coord_cartesian(ylim = c(1, 6), xlim = c(1, 6)) + scale_colour_manual(values = c("blue", "red"), labels=c('Wait-List Control',  'Mindful-Gratitude Practice')) + scale_fill_manual(values = c("blue", "red"))



```


Now I will specify and test a latent change score model.

```{r}
lcsm <- "
#Building parts
pre.t0=~a*ant_t0+b*sexT_t0+c*homo_t0+d*PreUK_t0
pre.t1=~a*ant_t1+b*sexT_t1+c*homo_t1+d*PreUK_t1

ant_t0~~ant_t1
sexT_t0~~sexT_t1
homo_t0~~homo_t1
PreUK_t0~~PreUK_t1

ant_t0 ~ ai*1
sexT_t0 ~ bi*1
homo_t0 ~ ci*1
PreUK_t0 ~ di*1

ant_t1 ~ ai*1
sexT_t1 ~ bi*1
homo_t1 ~ ci*1
PreUK_t1 ~ di*1

#Actual model

pre.t1~1*pre.t0
pre.t1~~0*pre.t1

delta=~1*pre.t1

delta~pre.t0

delta~NA*1
"


```

## LCSM test
```{r}
fit.lcsm <- cfa(lcsm,data=dat, estimator="mlr")
#fit.lcsm <- cfa(lcsm,data=dat, estimator="mlr", meanstructure = T, group = "group")
getFit(fit.lcsm)
summary(fit.lcsm, standardized =TRUE, fit.measures=TRUE, rsquare = T)
#parameterestimates(fit.lcsm)

```

So, that model works nicely. Now, I will not split into a multiple group model (too few cases). Instead, I will regress the change score (delta) on the group variable (like a t test).

## Group differences
### Model
```{r}
lcsm.group <- paste(lcsm, "delta~group", sep="\n")
cat(lcsm.group)
```

### Model test
```{r}
fit.lcsm.group <- cfa(lcsm.group,data=dat, estimator="mlr")
getFit(fit.lcsm.group)
summary(fit.lcsm.group, standardized =TRUE, fit.measures=TRUE, rsquare = T)
# parameterestimates(fit.lcsm.group)
```

Comparing different models (Hypothesis 3)
# Moderators terms

moderator term for collective narcissism

```{r}
dat$CNbyGroup <- scale(dat$CN_t0, center=TRUE, scale = FALSE)*scale(dat$group, center=TRUE, scale = FALSE)
```


moderator term for ingroup satisfaction
```{r}
dat$ISbyGroup <- scale(dat$IS_t0, center=TRUE, scale = FALSE)*scale(dat$group, center=TRUE, scale = FALSE)
```

moderator term for ingroup identification
```{r}
dat$SIbyGroup <- scale(dat$SI_t0, center=TRUE, scale = FALSE)*scale(dat$group, center=TRUE, scale = FALSE)
```
moderator term for social dominance orientation

```{r}
dat$SDObyGroup <- scale(dat$sdo_t0, center=TRUE, scale = FALSE)*scale(dat$group, center=TRUE, scale = FALSE)
```

moderator term for right-wing authoritarianism

```{r}
dat$RWAbyGroup <- scale(dat$RWA_t0, center=TRUE, scale = FALSE)*scale(dat$group, center=TRUE, scale = FALSE)
```

moderator term for individual narcissism

```{r}
dat$NPIbyGroup <- scale(dat$NPI_t0, center=TRUE, scale = FALSE)*scale(dat$group, center=TRUE, scale = FALSE)
```


### Model

Each block to be run separately for each model test

#CN
```{r}
lcsm.group.n <- paste(lcsm.group, "delta~CN_t0", "delta~CNbyGroup", sep="\n")
cat(lcsm.group.n)
```

#ID
```{r}
lcsm.group.n <- paste(lcsm.group, "delta~SI_t0", "delta~SIbyGroup", sep="\n")
cat(lcsm.group.n)
```

#SDO
```{r}
lcsm.group.n <- paste(lcsm.group, "delta~sdo_t0", "delta~SDObyGroup",  sep="\n")
cat(lcsm.group.n)
```

#RWA
```{r}
lcsm.group.n <- paste(lcsm.group, "delta~RWA_t0", "delta~RWAbyGroup",  sep="\n")
cat(lcsm.group.n)
```

#NPI
```{r}
lcsm.group.n <- paste(lcsm.group, "delta~NPI_t0", "delta~NPIbyGroup",  sep="\n")
cat(lcsm.group.n)
```


### Model test
To be run separately for each model specification including each moderator term
```{r}
fit.lcsm.group.n <- cfa(lcsm.group.n,data=dat, estimator="mlr")
getFit(fit.lcsm.group.n)
summary(fit.lcsm.group.n, standardized =TRUE, fit.measures=TRUE, rsquare = T)
s <- subset(parameterestimates(fit.lcsm.group.n, ci=TRUE, level=.95, standardized = T), parameterestimates(fit.lcsm.group.n, ci=TRUE)$lhs=="delta")
s %>% select(lhs, rhs, est, se, std.all, pvalue) #%>% flextable::flextable()
```


### Model test
```{r}

fit.lcsm.group.n <- cfa(lcsm.group.n,data=dat, estimator="mlr")
getFit(fit.lcsm.group.n)
summary(fit.lcsm.group.n, standardized =TRUE, fit.measures=TRUE, rsquare=TRUE)


```

Simple slopes following Preacher http://www.quantpsy.org/interact/mlr2.htm
```{r}

# 206 = df = 219 - 13
# squared standard errors
.220^2 #delta ~1 (intercept - b0) = .0484, coef = -.575
.041^2 #CN _t0  (b1) = .001681, coef = .055
.051^2 #group (b2) = .002601, coef = -.139
.076^2 #CN X Group (b3) = .005776, coef = -.229
# covariances
vcov(fit.lcsm.group.n)["delta~group", "delta~1"] # -0.0027804
vcov(fit.lcsm.group.n)["delta~CNbyGroup", "delta~CN_t0"] # .00083041

# 95% Confidence interval information for all parameters
parameterestimates(fit.lcsm.group.n, ci=TRUE, level=.9)
# 95% Confidence interval information for teh change score parameters only
s <- subset(parameterestimates(fit.lcsm.group.n, ci=TRUE, level=.95, standardized = T), parameterestimates(fit.lcsm.group.n, ci=TRUE)$lhs=="delta")

```


    TWO-WAY INTERACTION SIMPLE SLOPES OUTPUT

Your Input
=======================================================
  X1        = -2
  X2        = 2
  cv1       = 0
  cv2       = 1
  Intercept = -0.575
  X Slope   = 0.055
  Z Slope   = -0.139
  XZ Slope  = -0.229
  df        = 35
  alpha     = 0.05

Asymptotic (Co)variances
=======================================================
  var(b0) 0.0484
  var(b1) 0.001681
  var(b2) 0.002601
  var(b3) 0.005776
  cov(b2,b0) -0.0027804
  cov(b3,b1) 0.00083041

Simple Intercepts and Slopes at Conditional Values of Z
=======================================================
  At Z = cv1...
    simple intercept = -0.575(0.22), t=-2.6136, p=0.0131
    simple slope     = 0.055(0.041), t=1.3415, p=0.1884
  At Z = cv2...
    simple intercept = -0.714(0.2132), t=-3.3495, p=0.0019
    simple slope     = -0.174(0.0955), t=-1.8222, p=0.077

Points to Plot
=======================================================
  Line for cv1:  From {X=-2, Y=-0.685} to {X=2, Y=-0.465}
  Line for cv2:  From {X=-2, Y=-0.366} to {X=2, Y=-1.062}

*Regions of significance output suppressed because
 moderator is dichotomous.
 
 
```{r}
xx <- c(-2,2)   #  <-- change to alter plot dims
yy <- c(-1.2012,-0.366)   #  <-- change to alter plot dims
leg <- c(-2,-1.0968)   #  <-- change to alter legend location
x <- c(-2,2)   #  <-- x-coords for lines
y1 <- c(-0.685,-0.465)
y2 <- c(-0.366,-1.062)
plot(xx,yy,type='n',font=2,font.lab=2,xlab='X',ylab='Y',main='MLR 2-Way Interaction Plot')
lines(x,y1,lwd=3,lty=1,col=1)
lines(x,y2,lwd=3,lty=5,col=2)
points(x,y1,col=1,pch=16)
points(x,y2,col=1,pch=16)
legend(leg[1],leg[2],legend=c('CVz1(1)','CVz1(2)'),lwd=c(3,3),lty=c(1,5),col=c(1,2))
```
